%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wenneker Resume/CV
% LaTeX Template
% Version 1.1 (19/6/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%  PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[11pt]{article} % Font and paper size

\newcommand{\accentcolor}{RoyalBlue}

\input{../structure.tex} % Include the file specifying document layout and packages

%-------------------------------------------------------------------------------

\begin{document}

\userinformation % Print your information in the left column

\framebreak % End of the first column

%-------------------------------------------------------------------------------
%  HEADING
%-------------------------------------------------------------------------------

% \cvheading{Robert Detjens} % Large heading - your name
% \cvsubheading{DevOps / Sysadmin} % Subheading - your occupation/specialization

%-------------------------------------------------------------------------------
%  Cover Letter
%-------------------------------------------------------------------------------

\CVSection{Cover Letter}

%------------------------------------------------

\setlength{\parskip}{1em}

% Salutations [person],

% I am excited to see your job listing for [job title] at [company], which I saw on [job positing site]. [company] is a
% [good things about company]. I believe that my extensive experience in [industry] makes me an ideal candidate for this
% position at your company.

% As a recent graduate at Oregon State University, I have a significant background in [specialization]. I held multiple
% internships and held jobs focused on [focused job detail that applies to company]. [additional things that you want to
% highlight with your experience]

% You state in your job listing that you are looking for someone with [skill]. Throughout all four years of college,
% [experience that address skill]. I would love to bring my [experience] to a position with your [company].

% These strengths, combined with deep and varied academic, internship, and employment experience, have prepared me to make
% a strong and immediate impact at [company].

% I am excited about the opportunity to join the [company] as [good detail about company for reason you want to apply].
% Thank you for your time and consideration.

% Cordially yours,

% Huy Nguyen

% To whom read this cover letter,

% I am currently an undergraduate student at Oregon State University and current employee of the OSU Security Operation Center.
% As a detail-oriented and meticulous analyst, I am confident in my ability to perform in this position.

% During my role at the OSU SOC, I worked with large amounts of data, logs, and . I am an expert at seeing 
% through data to conclusions and crunching numbers. I often relied on my pristine communication skills to present my findings. 
% I was responsible for translating my data into an understandable format for others to read. I am vigilant in ensuring that my 
% data and findings are precise, and I can handle large volumes of data and mathematical problems with ease.

% During my academic career I studied a wide range of topics to support my statistics degree at Longford Tech. My college education 
% gave me access to topics such as probability, data computing, stochastic processes, game theory, machine learning, 
% sampling statistics, design and analysis of experiments, and calculus. I have always been a naturally inclined mathematics person, 
% but my college education furthered my knowledge and cemented important concepts into my working memory. My education 
% has allowed to perfect my skills as a mathematician and as a team player. I possess an impeccable work ethic and am able to 
% meet tight deadlines.

% Thank you for your time and consideration. I look forward to hearing more about River Tech and the Analyst role.

To whomever reads the cover letter,

I am an undergraduate student at Oregon State University and current employee in OSU Security Operation Center,
who is looking towards a future career in Cybersecurity. During my student analyst role at the OSU SOC, I have worked with 
many different tools to combat against attackers, and processed large amounts of data and logs to investigate compromised
machines and users. In addition to this, I also have been engaged in threat hunting within the university's network for surging
of CVEs.

Outside of work, I have been an active member of OSU's Security Club (OSUSEC) where I participated in activities involving 
security related challenges. Furthermore, I was a part of both the PRCCDC and CyberForce teams and had more in-depth experience 
related to hardening systems against attackers. My membership in the club has helped cement my skills and contribute towards a 
Cybersecurity career.

With the experience I have accumulated, and my passion for the field, I strongly believe that I would be a strong asset and 
team player to the Security Operations Center, and be a leader for the students working in the SOC. OSU has given me many opportunities,
skills and friends, and with this rare opportunity, I want to give back to ensure other students will get the same experience as I do. 
In particular, I will be able to apply the knowledge and experience I have acquired from classes and various club activities. 
In addition to my technical abilities and drive to learn more, I have prior experience in the field and work well with others. 
For instance, the team I participated with placed 7th in the PRCCDC Cybersecurity Competition in 2021, placed 1st regionally in the DOE 
Cyberforce Competition in 2022 and placed 1st in PRCCDC Cybersecurity Competition in 2022. From this, the team managed to
participated in the NCCDC Cybersecurity Competition, and placed 5th for our first year. These experiences from CDCs allowed me 
to gain further insight into Cybersecurity, but also gave me a stepping stone to understand how to react effectively as an 
individual contributor and team member. I have also demonstrated the ability to adapt in stressful situations, and strive to 
learn new techniques I can apply in my career. While I strongly believe that I have the foundational knowledge and experience 
with security tools required for the job, I am willing to put in additional effort to learn new tools and skills required to 
further succeed in the role. With these qualifications and accomplishments, I am looking forward to be working in 
a team setting and contributing to OSU's secured future. 

Thank you for your consideration,
	
Huy Nguyen

%------------------------------------------------

\end{document}
